### 2024-07-23 data-visualization.qmd
20240722 - confidence interval

A histogram of fantasy points with an overlaid density plot is depicted in @fig-histogramDensity.

```{r}
#| label: fig-histogramDensity
#| fig-cap: "Histogram with Overlaid Density Plot."

@@

```{r}
player_stats_seasonal_offense_summary <- player_stats_seasonal_offense %>%
    filter(position_group %in% c("QB","RB","WR","TE")) %>% 
  group_by(position_group) %>%
  summarise( 
    n = sum(!is.na(fantasy_points)),
    mean = mean(fantasy_points, na.rm = TRUE),
    sd = sd(fantasy_points, na.rm = TRUE)
  ) %>%
  mutate(se = sd/sqrt(n)) %>%
  mutate(
    ci_lower = mean - qt(0.975, df = n - 1) * se,
    ci_upper = mean + qt(0.975, df = n - 1) * se
  )
```

>>>>

A histogram of fantasy points with an overlaid density and rug plot is depicted in @fig-histogramDensity.

```{r}
#| label: fig-histogramDensity
#| fig-cap: "Histogram with Overlaid Density and Rug Plot."

@@

```{r}
confidenceLevel <- .95 # for 95% confidence interval

player_stats_seasonal_offense_summary <- player_stats_seasonal_offense %>%
    filter(position_group %in% c("QB","RB","WR","TE")) %>% 
  group_by(position_group) %>%
  summarise( 
    n = sum(!is.na(fantasy_points)),
    mean = mean(fantasy_points, na.rm = TRUE),
    sd = sd(fantasy_points, na.rm = TRUE)
  ) %>%
  mutate(se = sd/sqrt(n)) %>%
  mutate(
    ci_lower = mean - qt(p = 1 - (1 - confidenceLevel) / 2, df = n - 1) * se,
    ci_upper = mean + qt(p = 1 - (1 - confidenceLevel) / 2, df = n - 1) * se
  )
```
